---
title: "Data visualisation"
author: "Alina Ismagilova"
date: "2021-22-09"
output: github_document

---
```{r}
library(ggplot2)
library(dplyr)
library(rmarkdown)
```

```{r}
url <- "https://raw.githubusercontent.com/lukaseamus/marine-microplastic/main/STOTEN/fragments.csv"
download.file(url, destfile = basename(url)) 
```
```
```{r}
fragments <- read.csv("fragments.csv")
```


```{r}
ggplot(data = fragments, aes(x = polymer, y = fragments, fill = use)) +
  geom_col(color = 'black',  size = 0.3, width = 0.5, position = 'dodge') +
  facet_wrap(~diameter) +
  ylab(expression("Abraded microplastic fragments (m"^-1*")"))
ggsave(file="graph1.png")
```

```{r}
ggplot(data = fragments, aes(x = polymer, y = mass, fill = use)) +
  geom_col(color = 'black',  size = 0.3, width = 0.5, position = 'dodge') +
  facet_wrap(~diameter) +
  ylab(expression("Abraded microplastic mass ("*mu*"g m"^-1*")"))
ggsave(file="graph2.png")
```

```{r}
ggplot(data = fragments, aes(x = polymer, y = density, fill = use)) +
  geom_col(color = 'black',  size = 0.3, width = 0.5, position = 'dodge') +
  facet_wrap(~diameter)
ggsave(file="graph3.png")
```

```{r}
ggplot(data = fragments, aes(x = polymer, y = fragment.volume, fill = use)) +
  geom_col(color = 'black',  size = 0.3, width = 0.5, position = 'dodge') +
  facet_wrap(~diameter)
ggsave(file="graph4.png")
```





